Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Benjamin's comments handled

Some of the other mechanisms listed above should also be amenable to strong
formal guarantees.  In particular, Roessler and DeHon
\cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies~\cite{pump_oakland2015} for stack safety that aim to offer
universal protection.  But the reasoning involved is somewhat subtle.
Their most realistic micro-policy, called Lazy
Tagging and Clearing ({\LTC}\bcp{does it have to be italic?}), makes an interesting performance
trade-off: it allows function activations to write improperly into one
another's stack frames, but ensures that the owner of the corrupted
memory cannot access it afterward.
%
Under this policy, one function activation {\em can} corrupt another's
memory---just not in ways that affect observable behavior.
Therefore, {\LTC} would not fulfill Georges et al.'s property
(adapted to the tagged setting).  But {\LTC} does
arguably enforce stack safety.  A looser, more observational
definition of stack safety is needed to fit this situation.

@@

Our properties are stated abstractly in the hope that they can also be
applied to other enforcement mechanisms besides \LTC.
%
However, it does not seem feasible to give
a universal definition of stack safety
that applies to all architectures and compilers.
While many security properties can be described purely at
the level of a high-level programming language and translated to a
target machine by a secure compiler, stack safety cannot be defined in
this way, since ``the stack'' is not explicitly present in the
definitions of most source languages but rather is implicit in the semantics
of features such as calls and returns.\footnote{
Contrast Azevedo de
  Amorim et al.'s work on heap safety
  \cite{DBLP:conf/post/AmorimHP18}, where the concept of the heap figures
  directly in high-level language semantics and its security is
  therefore amenable to a high-level treatment.}
%
But neither can stack safety be described coherently as a purely
low-level property;
indeed, at the lowest level, the specification of a ``well-behaved
stack'' is almost vacuous. The ISA is not concerned with such
questions as whether a caller's frame should be readable or writable
to its callee. Those are the purview of high-level languages built
atop the hardware stack.

Thus, any low-level treatment of stack safety must begin by asking:
which high-level features are supported in a given
setting using the stack, and what are their
security requirements? Different answers will beget different properties.
\bcp{There's an awkward conceptual transition here: We pose a question
(``which high-level features are supported in a given
setting using the stack, and what are their
security requirements'') but then we don't seem to be going ahead and
answering it.  I suggest adding a sentence here that answers the
question directly, then a paragraph break.} \bcp{Though, actually, the
next sentence repeats points that have already been made above.  Maybe
better to just delete it and find a new transition to the sentence
after.}
We identify and define five security requirements that a system might try
to enforce upon a function call: well-bracketed control flow, and the
integrity and confidentiality of each of the caller and the callee.
%
We apply these first to a simple system
with very few features, then to a more realistic one supporting
tail-call elimination, argument passing on the stack, and callee-save
registers.

We demonstrate the usefulness of our properties for distinguishing
between correct and
incorrect enforcement using
QuickChick~\cite{Denes:VSL2014,Pierce:SF4}, a property-based
random testing tool for Coq.
Indeed, we find that the published version of {\LTC} is flawed in
a way that undermines both integrity and confidentiality; after
correcting this flaw, {\LTC} satisfies all our
properties.  Further, we modify {\LTC} to protect the features of
our more realistic system and apply
random testing to validate this extended protection mechanism against
the extended properties.

%We generate random programs, using the features of our
%more realistic system, and check that the stack safety {\em micro-policies}
%of Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}
%correctly detect the ones that attempt to violate one of our properties.

%Furthermore, we
%check that the testing framework is able to generate counterexamples
%that violate our properties but are \emph{not} halted by incorrect
%variants of the enforcement mechanisms---including the original {\LTC}!
% SNA: we talk about this in the testing section, and it's a "best practice" for
% PBT, but not really a contribution in and of itself

%\subsection{Contributions}

@@

Stack safety properties need to describe the behavior of machine code, but they naturally
talk about function activations and stack contents---abstractions that
are typically not visible at machine level. To bridge this gap,
our properties are defined in terms of a {\em security semantics} layered on top of
the standard execution semantics of the machine.  The security semantics identifies certain
state transitions of the machine as {\em security-relevant operations}, which update
a notional {\em security context}.  This context consists of
an (abstract) stack of function activations, each associated with a {\em view}
that maps each machine {\em state element} (memory location or register)
to a {\em security class} (active, sealed, etc.) specifying how the activation
can access the element.
The action of a security-relevant operation on the context is defined by a set
of rules that characterize how particular machine code sequences are used
to implement the function abstraction in terms of the stack and registers.\bcp{OK?}

@@

\paragraph*{Machine Model}
We assume a conventional ISA (e.g., RISC-V, x86-64, etc.), with registers including a program counter
and stack pointer.
%, and a standard ABI.
%\sna{Not in our formalism (hardcoded +4 in the definition of WBCF notwithstanding.)
%  This assumption is made in our example and testing.}
We make no particular assumptions about the provenance of the machine code; in particular,
we do not assume any particular compiler.
If the machine is enhanced with % security
enforcement mechanisms such as hardware
tags~\cite{pump_hasp2014,Gollapudi+23} or
capabilities~\cite{Woodruff+14}, we
assume that the behavior of these mechanisms is incorporated into the basic
step semantics of the machine, but we keep the enforcement state
unchanged when constructing variant states\bcp{As a reader, I wonder
  ``How would they do that?  Seems like they are saying the tag
  enforcement or whatever is just part of the basic machine step
  relation and we can't see it, but then going on to place a
  requirement on it. How would such a requirement be phrased, formally?''}.
Failstop behavior by enforcement mechanisms is modeled as stepping to the same state
(and thus silently diverging).
%% \sna{I think that the payload concept is too nitty-gritty for this section.
%%   The chief use of the payload is that it allows every value to be interpreted
%%   as an address. In the tag world, it happens to coincide with a natural instance
%%   of our variant-compatibility relation.}

@@

\begin{table}
\begin{center}
  \begin{tabular}{| l | l | l |}
    \hline
    Operation \(\psi \in \Psi\) & Parameters & Sections\\
    \hline
    \example \(\mathbf{call}\) & target address, argument registers & \ref{sec:example},\ref{sec:formal}\\
    \testing & stack arguments (base, offset \& size) & \ref{sec:extensions},\ref{sec:testing} \\
    \example \(\mathbf{return}\) & & \ref{sec:example},\ref{sec:formal}\\
    \example \(\mathbf{alloc}\) & offset \& size & \ref{sec:example},\ref{sec:formal}\\
    \testing & public flag & \ref{sec:extensions},\ref{sec:testing} \\
    \example \(\mathbf{dealloc}\) & offset \& size &  \ref{sec:example},\ref{sec:formal}\\
    \testing \(\mathbf{tail call}\) & (same as for \(\mathbf{call}\)) & \ref{sec:extensions},\ref{sec:testing} \\
%    \hline
%    \multicolumn{2}{|c|}{{\it Pointer provenance operations}} \\
%    \hline
    \theory \(\mathbf{promote}\) & register, offset \& size & \ref{app:ptr} \\
    \theory \(\mathbf{propagate}\) & source register/address & \ref{app:ptr} \\
    \theory & destination register/address & \ref{app:ptr} \\
    \theory \(\mathbf{clear}\) & target register/address & \ref{app:ptr} \\
    \hline
  \end{tabular}
\end{center}
\caption{Security-relevant operations and their parameters, with the
  sections where
  they are first used.  \bcp{Say what the gray levels mean.}}
  \label{tab:psi}
\end{table}

@@

We do not assume that low-level code adheres to any fixed\bcp{single?
(I think we do assume that the calling convention is fixed in any
particular instance of our framework, no?)} calling
convention or is being used to implement any particular
source-language constructs.
Indeed, if the source language is C, then high-level programs might
contain undefined behavior, in which case they might be compiled to
arbitrary machine code. A given enforcement mechanism or target
architecture might place additional constraints, particularly on
call and return sequences.\bcp{Not sure that last sentence is helpful.}

@@

The C code is compiled using the standard RISC-V calling conventions~\cite{RISC-V-CC}.
In particular, the function's first argument and its
return value are both passed in {\tt a0}.
Memory is byte addressed, and the stack grows towards
lower addresses. We assume that {\tt main} begins at address 0 and its
callee {\tt f} at address 100.  \bcp{What are alloc(-20,20) and
  dealloc(0,20)? What is $\varepsilon$ in call $\varepsilon$?  Also, readers who don't have the RISCV ISA at their
fingertips may wonder what all the instructions actually do.  We
should (if it's true) explicitly say that they don't need to worry
about the details.}

@@

We implement and test two micro-policies inspired by
Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} ({\LTC}).
Their precise connection to Roessler and DeHon's work is discussed below.
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and while the activation is running, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). Stack locations not part of
any activation are tagged \(\tagNoDepth\).

In \(DI\), \(n\) always corresponds to the depth of the stack when
the function is called. A function must initialize its entire frame upon entry
in order to tag it, and then clear the frame before returning.
During normal execution, the micro-policy rules only permit load and
store operations when the target memory is tagged {\em with the same depth}
as the current {\PCname} tag, or, for store operations, if the target memory
is tagged \(\tagNoDepth\).

In {\LTC}, a function neither initializes the frame at entry nor clears it at exist;
instead, it simply sets each location's tag to the PC tag when that location is written. It does
not check if those writes are legal! If the PC tag is \(\tagPCDepth{n}\),
then any stack location that recieves a store will be tagged \(\tagStackDepth{n}\).
On a load, the micro-policy failstops if the source memory location
is tagged \(\tagNoDepth\) or \(\tagStackDepth{n}\) for some \(n\) that
doesn't match the PC tag.

@@

For Roessler and DeHon (henceforward \emph{R\&D}), Lazy Tagging and Lazy Clearing are both optimizations that
can be applied to their Depth Isolation policy. Our version of {\LTC}
corresponds to Depth Isolation with both optimizations applied. How closely
do our properties correspond to the specifications of their policies?

R\&D differentiate between memory safety policies (without lazy optimization)
and {\em data-flow integrity} policies (with lazy optimization). Our properties
are phrased in terms of data flow, and we apply them to both optimized and non-optimized
Depth Isolation.
R\&D do not attempt to define explicit formal properties, but they do list the
behaviors that they expect their data-flow integrity policies to prevent, namely:
reads from sealed objects
(our \(\clrc\)), writes to sealed objects
if they are later read (our \(\clri\)), and reads
from deallocated objects (our \(\clec\)).
They also note that Lazy Clearing prevents uninitialized reads,
which corresponds roughly to our \(\clei\).

@@

R\&D propose addressing the dangling-pointer issue by
tracking both the depth of the current activation and the static identity
of the active function. This would not eliminate all instances of this issue, but it
would require the confidentiality-violating activation to be of the same
function that wrote the data in the first place, which is a significantly higher bar.
We propose instead tracking every activation uniquely, which should eliminate the
issue entirely---and does in our tests.

@@

R\&D do not need to protect registers, since they include the compiler in their
trusted computing base, but we target threat models that do not.
In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and {\LTC}
so that callee-saved registers are also tagged with the color of the
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in {\LTC} they are tagged when a value is placed in them.

@@

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
  Bug & Property Violated & MTTF (s) & Tests \\
  \hline
      {\em LOAD\_NO\_CHECK\_DI}  & Confidentiality & 24.2 & 13.3 \\
      {\em STORE\_NO\_CHECK} & Integrity & 26.9 & 26 \\
      {\em HEADER\_NO\_INIT} & Integrity & 69.5 & 76.3 \\
  \hline
  \hline
      {\em PER\_DEPTH\_TAG} & Integrity & 189.7 & 8342.5  \\
      {\em LOAD\_NO\_CHECK\_LT}  & Integrity & 23.5 & 12.0 \\
      {\em LOAD\_NO\_CHECK\_LT}  & Confidentiality & 19.2 & 695.5 \\
      {\em STORE\_NO\_UPDATE} & Integrity & 70 & 80.6  \\
      {\em STORE\_NO\_UPDATE} & Confidentiality & 4.9 & 88.5 \\
  \hline
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous \(DI\) (top) and {\LTC} (bottom) micro-policies}
\vspace*{-2em}
\label{tab:bug-table}
\end{table}

@@

For {\LTC}, the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking longer to catch.

@@

To our knowledge, the only other line of work that aims to rigorously characterize the
security of the stack is the StkTokens-Cerise family of CHERI-enforced secure calling
conventions \cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
%
The authors define stack safety as overlay semantics and related stack
safety properties, phrased in terms of logical relations instead of trace
properties.
%
Originally, they define an informal notion of stack safety as the combination of WBCF
and ``local state encapsulation''~\cite{SkorstengaardSTKJFP},
and describe the latter
in terms of integrity only (but it has confidentiality, equivalent
to \(\clri\) {\em and} \(\clrc\)).
%
StkTokens \cite{SkorstengaardSTKJFP} makes this conception of stack safety
explicit through an overlay semantics
%(that internalizes the semantics of the calling convention and is proved fully
%abstract w.r.t. the concrete machine executing the actual calling convention).
%This overlay manipulates an abstract call stack whose elements are frames. A
%function call creates a new stack frame off of a capability representing the
%available stack space, and a function return merges the corresponding frame
%back into the stack capability. It is assumed that components do not leave any
%capabilities on the stack when they return.
which (1) on call mints new a stack frame from a capability representing the
available stack space, and (2) on return merges the current frame back into the
stack capability, under the assumption that there are no capabilities left on
the stack.

Their latest
paper \cite{Georges22:TempsDesCerises} was inspired by the properties presented
in this paper to extend their formalism to include confidentiality. When
checking if our properties applied to their old calling convention, they noted that
it did not enforce \(\clec\), and made sure that their new version
would in addition to building it into their formalism
\cite{Georges22:personalcommunication}.
%
To do so, they redesign the overlay semantics to actually pop stack frames on
return and have them disappear from the stack.
%
This demonstrates the benefit of our
choice to explicitly state properties in security terms: specifying security
is hard, and when the spec takes the form of a ``correct by
construction'' machine, it is easy to neglect a non-obvious security
requirement.

% \cite{Georges22:TempsDesCerises} revisits this design and modifies the
% overlay in an interesting way to actually pop stack frames on return and have
% them disappear from the stack rather than be merged back into it. It thus
% realizes callee confidentiality (and no dangling stack pointers).

>>>>

Some of the other mechanisms listed above should also be amenable to strong
formal guarantees.  In particular, Roessler and DeHon
\cite{DBLP:conf/sp/RoesslerD18} present an array of tag-based
micro-policies~\cite{pump_oakland2015} for stack safety that aim to offer
universal protection.  But the reasoning involved can be subtle:
they include micro-policy optimizations, Lazy Tagging and Lazy Clearing
(likely to be deployed together, which we hereafter refer to as Lazy
Tagging and Clearing, or LTC). LTC allows function activations to write
improperly into one another's stack frames, but ensures that the owner of
the corrupted memory cannot access it afterward, avoiding expensive
clearings of the stack frame.
%
Under this policy, one function activation {\em can} corrupt another's
memory---just not in ways that affect observable behavior.
Therefore, LTC would not fulfill Georges et al.'s property
(adapted to the tagged setting).  But LTC does arguably enforce stack safety,
or as Roessler and DeHon describe it informally, a sort of data-flow
integrity tied to the stack. A looser, more observational
definition of stack safety is needed to fit this situation.

@@

Our properties are stated abstractly in the hope that they can also be
applied to other enforcement mechanisms besides LTC.
%
However, it does not seem feasible to give
a universal definition of stack safety
that applies to all architectures and compilers.
While many security properties can be described purely at
the level of a high-level programming language and translated to a
target machine by a secure compiler, stack safety cannot be defined in
this way, since ``the stack'' is not explicitly present in the
definitions of most source languages but rather is implicit in the semantics
of features such as calls and returns.\footnote{
Contrast Azevedo de
  Amorim et al.'s work on heap safety
  \cite{DBLP:conf/post/AmorimHP18}, where the concept of the heap figures
  directly in high-level language semantics and its security is
  therefore amenable to a high-level treatment.}
%
But neither can stack safety be described coherently as a purely
low-level property;
indeed, at the lowest level, the specification of a ``well-behaved
stack'' is almost vacuous. The ISA is not concerned with such
questions as whether a caller's frame should be readable or writable
to its callee. Those are the purview of high-level languages built
atop the hardware stack.

Thus, any low-level treatment of stack safety must begin by asking:
which high-level features are supported in a given
setting using the stack, and how does their presence influence
the expectation of well-bracketed control flow, confidentiality,
and integrity? We begin with a simple system
with very few features, then move to a more realistic one supporting
tail-call elimination, argument passing on the stack, and callee-save
registers. Our properties are factored so that the basic structure
of each of our five properties remains constant while the presence or
absence of different features leads to subtler differences in how
they behave.

We demonstrate the usefulness of our properties for distinguishing
between correct and
incorrect enforcement using
QuickChick~\cite{Denes:VSL2014,Pierce:SF4}, a property-based
random testing tool for Coq.
Indeed, we find that the published version of LTC is flawed in
a way that undermines both integrity and confidentiality; after
correcting this flaw, LTC satisfies all of our
properties.  Further, we modify LTC to protect the features of
our more realistic system and apply
random testing to validate this extended protection mechanism against
the extended properties.

@@

Stack safety properties need to describe the behavior of machine code, but they naturally
talk about function activations and stack contents---abstractions that
are typically not visible at machine level. To bridge this gap,
our properties are defined in terms of a {\em security semantics} layered on top of
the standard execution semantics of the machine.  The security semantics identifies certain
state transitions of the machine as {\em security-relevant operations}, which update
a notional {\em security context}.  This context consists of
an (abstract) stack of function activations, each associated with a {\em view}
that maps each machine {\em state element} (memory location or register)
to a {\em security class} (active, sealed, etc.) specifying how the activation
can access the element.
The action of a security-relevant operation on the context is defined by a function
that characterizes how the operation's underling machine code ought to
implement the function abstraction in terms of the stack and registers.

@@

\paragraph*{Machine Model}
We assume a conventional ISA (e.g., RISC-V, x86-64, etc.), with registers including a program counter
and stack pointer.
%, and a standard ABI.
%\sna{Not in our formalism (hardcoded +4 in the definition of WBCF notwithstanding.)
%  This assumption is made in our example and testing.}
We make no particular assumptions about the provenance of the machine code; in particular,
we do not assume any particular compiler.
If the machine is enhanced with % security
enforcement mechanisms such as hardware
tags~\cite{pump_hasp2014,Gollapudi+23} or
capabilities~\cite{Woodruff+14}, we
assume that the behavior of these mechanisms is incorporated into the basic
step semantics of the machine, with a notion of ``compatible'' states that
share security behavior that may be defined based on the enforcement mechanism.
Failstop behavior by enforcement mechanisms is modeled as stepping to the same state
(and thus silently diverging).
%% \sna{I think that the payload concept is too nitty-gritty for this section.
%%   The chief use of the payload is that it allows every value to be interpreted
%%   as an address. In the tag world, it happens to coincide with a natural instance
%%   of our variant-compatibility relation.}

@@

\begin{table}
\begin{center}
  \begin{tabular}{| l | l | l |}
    \hline
    Operation \(\psi \in \Psi\) & Parameters & Sections\\
    \hline
    \example \(\mathbf{call}\) & target address, argument registers & \ref{sec:example},\ref{sec:formal}\\
    \testing & stack arguments (base, offset \& size) & \ref{sec:extensions},\ref{sec:testing} \\
    \example \(\mathbf{return}\) & & \ref{sec:example},\ref{sec:formal}\\
    \example \(\mathbf{alloc}\) & offset \& size & \ref{sec:example},\ref{sec:formal}\\
    \testing & public flag & \ref{sec:extensions},\ref{sec:testing} \\
    \example \(\mathbf{dealloc}\) & offset \& size &  \ref{sec:example},\ref{sec:formal}\\
    \testing \(\mathbf{tail call}\) & (same as for \(\mathbf{call}\)) & \ref{sec:extensions},\ref{sec:testing} \\
%    \hline
%    \multicolumn{2}{|c|}{{\it Pointer provenance operations}} \\
%    \hline
    \theory \(\mathbf{promote}\) & register, offset \& size & \ref{app:ptr} \\
    \theory \(\mathbf{propagate}\) & source register/address & \ref{app:ptr} \\
    \theory & destination register/address & \ref{app:ptr} \\
    \theory \(\mathbf{clear}\) & target register/address & \ref{app:ptr} \\
    \hline
  \end{tabular}
\end{center}
\caption{Security-relevant operations and their parameters, with the
  sections where they are first defined or used. Entries in light grey do not appear in
  our examples, but are part of our testing. Dark grey entries are not tested.}
\label{tab:psi}
\end{table}

@@

We do not assume that low-level code adheres to any single calling
convention or is being used to implement any particular
source-language constructs.
Indeed, if the source language is C, then high-level programs might
contain undefined behavior, in which case they might be compiled to
arbitrary machine code.

@@

The C code is compiled using the standard RISC-V calling conventions~\cite{RISC-V-CC}.
In particular, the function's first argument and its
return value are both passed in {\tt a0}.
Memory is byte addressed, and the stack grows towards
lower addresses. We assume that {\tt main} begins at address 0 and its
callee {\tt f} at address 100. The annotations in the right-hand column are
security-relevant operations, described further below.
The assembly is a simplified but otherwise typical compilation of the
source code into RISC-V; its details are less important than the positions
of the security-relevant operations.

@@

We implement and test two micro-policies inspired by
Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}:
{\em Depth Isolation} without lazy optimizations (DI) and with both
Lazy Tagging and Lazy Clearing optimizations (LTC).
(The connection between our properties and Roessler and DeHon's work is discussed below.)
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and while the activation is running, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). Stack locations not part of
any activation are tagged \(\tagNoDepth\).

In DI, \(n\) always corresponds to the depth of the stack when
the function is called. A function must initialize its entire frame upon entry
in order to tag it, and then clear the frame before returning.
During normal execution, the micro-policy rules only permit load and
store operations when the target memory is tagged {\em with the same depth}
as the current {\PCname} tag, or, for store operations, if the target memory
is tagged \(\tagNoDepth\).

In LTC, a function neither initializes the frame at entry nor clears it at exist;
instead, it simply sets each location's tag to the PC tag when that location is written. It does
not check if those writes are legal! If the PC tag is \(\tagPCDepth{n}\),
then any stack location that recieves a store will be tagged \(\tagStackDepth{n}\).
On a load, the micro-policy failstops if the source memory location
is tagged \(\tagNoDepth\) or \(\tagStackDepth{n}\) for some \(n\) that
doesn't match the PC tag.

@@

Roessler and DeHon (henceforward \emph{R\&D})
R\&D differentiate between memory safety policies (without lazy optimization)
and {\em data-flow integrity} policies (with lazy optimization). Our properties
are phrased in terms of data flow, and we apply them to both optimized and non-optimized
Depth Isolation.
R\&D do not attempt to define explicit formal properties, but they do list the
behaviors that they expect their data-flow integrity policies to prevent, namely:
reads from sealed objects
(our \(\clrc\)), writes to sealed objects
if they are later read (our \(\clri\)), and reads
from deallocated objects (our \(\clec\)).
They also note that Lazy Clearing prevents uninitialized reads,
which corresponds roughly to our \(\clei\).

@@

They propose addressing the dangling-pointer issue by
tracking both the depth of the current activation and the static identity
of the active function. This would not eliminate all instances of this issue, but it
would require the confidentiality-violating activation to be of the same
function that wrote the data in the first place, which is a significantly higher bar.
We propose instead tracking every activation uniquely, which should eliminate the
issue entirely---and does in our tests.

@@

R\&D do not need to protect registers, since they include the compiler in their
trusted computing base, but we target threat models that do not.
In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend DI and LTC
so that callee-saved registers are also tagged with the color of the
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in LTC they are tagged when a value is placed in them.

@@

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
  Bug & Property Violated & MTTF (s) & Tests \\
  \hline
      {\em LOAD\_NO\_CHECK\_DI}  & Confidentiality & 24.2 & 13.3 \\
      {\em STORE\_NO\_CHECK} & Integrity & 26.9 & 26 \\
      {\em HEADER\_NO\_INIT} & Integrity & 69.5 & 76.3 \\
  \hline
  \hline
      {\em PER\_DEPTH\_TAG} & Integrity & 189.7 & 8342.5  \\
      {\em LOAD\_NO\_CHECK\_LT}  & Integrity & 23.5 & 12.0 \\
      {\em LOAD\_NO\_CHECK\_LT}  & Confidentiality & 19.2 & 695.5 \\
      {\em STORE\_NO\_UPDATE} & Integrity & 70 & 80.6  \\
      {\em STORE\_NO\_UPDATE} & Confidentiality & 4.9 & 88.5 \\
  \hline
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous micro-policies: DI (top) and LTC (bottom)}
\vspace*{-2em}
\label{tab:bug-table}
\end{table}

@@

For LTC, the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking longer to catch.

@@

To our knowledge, the only other line of work that aims to rigorously characterize the
security of the stack is the StkTokens-Cerise family of CHERI-enforced secure calling
conventions \cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
%
The authors define stack safety as overlay semantics and related stack
safety properties, phrased in terms of logical relations instead of trace
properties.
%
Originally, they describe ``local state encapsulation''~\cite{SkorstengaardSTKJFP}
in terms of integrity only (but it has confidentiality, equivalent
to \(\clri\) {\em and} \(\clrc\)). Their latest
paper \cite{Georges22:TempsDesCerises} was inspired by the properties presented
in this paper to extend their formalism to include confidentiality. When
checking if our properties applied to their old calling convention, they noted that
it did not enforce \(\clec\), and made sure that their new version
would in addition to building it into their formalism
\cite{Georges22:personalcommunication}. This demonstrates the benefit of our
choice to explicitly state properties in security terms: specifying security
is hard, and when the spec takes the form of a ``correct by
construction'' machine, it is easy to neglect a non-obvious security
requirement.
